---
title: "Quiz2"
author: "Lawrence Lau"
date: "July 23, 2015"
output: html_document
---

```{r}
library(stringi)
library(tm)
library(quanteda)
source('~/datasciencecoursera/Courses/Capstone/capstoneproject/ngramTailFinder.R')
source('~/datasciencecoursera/Courses/Capstone/capstoneproject/NextWordPredictor.R')
source('~/datasciencecoursera/Courses/Capstone/capstoneproject/ngramTailFinder1.R')
```

For each of the sentence fragments below use your natural language processing algorithm to predict the next word in the sentence. 

1.) The guy in front of me just bought a pound of bacon, a bouquet, and a case of


beer
pretzels
soda
cheese

```{r}
NextWordPredictor("The guy in front of me just bought a pound of bacon, a bouquet, and a case of", 3, " ")
```

beer

2.) You're the reason why I smile everyday. Can you follow me please? It would mean the


best
universe
world
most

```{r}
NextWordPredictor("You're the reason why I smile everyday. Can you follow me please? It would mean the", 4, " ")
```



3.)  Hey sunshine, can you follow me and make me the


happiest
smelliest
bluest
saddest

```{r}
NextWordPredictor("Hey sunshine, can you follow me and make me the", 4, " ")
```



4.)  Very early observations on the Bills game: Offense still struggling but the


defense
players
crowd
referees

```{r}
NextWordPredictor("Very early observations on the Bills game: Offense still struggling but the", 4, " ")
```



5.)  Go on a romantic date at the


beach
grocery
movies
mall

```{r}
NextWordPredictor("Go on a romantic date at the", 4, " ")
```
