---
title: "Quiz2"
author: "Lawrence Lau"
date: "July 23, 2015"
output: html_document
---

```{r}
library(stringi)
library(tm)
library(quanteda)
source('~/datasciencecoursera/Courses/Capstone/capstoneproject/ngramTailFinder.R')
source('~/datasciencecoursera/Courses/Capstone/capstoneproject/NextWordPredictor.R')
source('~/datasciencecoursera/Courses/Capstone/capstoneproject/ngramTailFinder1.R')
```

For each of the sentence fragments below use your natural language processing algorithm to predict the next word in the sentence. 

1.) The guy in front of me just bought a pound of bacon, a bouquet, and a case of


beer
pretzels
soda
cheese

```{r}
NextWordPredictor("The guy in front of me just bought a pound of bacon, a bouquet, and a case of", 3, " ")
```

beer

2.) You're the reason why I smile everyday. Can you follow me please? It would mean the


best
universe
world
most

```{r}
NextWordPredictor("You're the reason why I smile everyday. Can you follow me please? It would mean the", 3, " ")
```

world

3.)  Hey sunshine, can you follow me and make me the


happiest
smelliest
bluest
saddest

```{r}
NextWordPredictor("Hey sunshine, can you follow me and make me the", 3, " ")
```

happiest

4.)  Very early observations on the Bills game: Offense still struggling but the


defense
players
crowd
referees

```{r}
system.time(NextWordPredictor("offense", 1, " "))
```

defense

5.)  Go on a romantic date at the


beach
grocery
movies
mall

```{r}
NextWordPredictor("Go on a romantic date at the", 2, " ")
```

beach

6.)  Well I'm pretty sure my granny has some old bagpipes in her garage I'll dust them off and be
on my

phone
way
motorcycle
horse

```{r}
NextWordPredictor("Well I'm pretty sure my granny has some old bagpipes in her garage I'll dust them off and be on my", 2, " ")
```

way

7.) Ohhhhh #PointBreak is on tomorrow. Love that film and haven't seen it in quite some

thing
weeks
years
time

```{r}
NextWordPredictor("Ohhhhh #PointBreak is on tomorrow. Love that film and haven't seen it in quite some", 2, " ")
```

time

8.)  After the ice bucket challenge Louis will push his long wet hair out of his eyes with his little

toes
eyes
ears
fingers

```{r}
NextWordPredictor("After the ice bucket challenge Louis will push his long wet hair out of his eyes with his little", 4, " ")
```

ears

9.)  Be grateful for the good times and keep the faith during the

bad
sad
hard
worse

```{r}
NextWordPredictor("Be grateful for the good times and keep the faith during the", 4, " ")
```



10.)  If this isn't the cutest thing you've ever seen, then you must be

insane
asleep
insensitive
callous

```{r}
NextWordPredictor("If this isn't the cutest thing you've ever seen, then you must be", 4, " ")
```


