---
title: "Quiz2"
author: "Lawrence Lau"
date: "July 23, 2015"
output: html_document
---

```{r}
library(stringi)
library(tm)
library(quanteda)
source('~/datasciencecoursera/Courses/Capstone/capstoneproject/ngramTailFinder.R')
source('~/datasciencecoursera/Courses/Capstone/capstoneproject/NextWordPredictor.R')
source('~/datasciencecoursera/Courses/Capstone/capstoneproject/ngramTailFinder1.R')
```

For each of the sentence fragments below use your natural language processing algorithm to predict the next word in the sentence. 

1.) The guy in front of me just bought a pound of bacon, a bouquet, and a case of


beer
pretzels
soda
cheese

```{r}
a <- NextWordPredictor("The guy in front of me just bought a pound of bacon, a bouquet, and a case of", 2, " ")
a[grepl("beer", names(a))] # beer = 28

```

confirmd answer is beer

2.) You're the reason why I smile everyday. Can you follow me please? It would mean the


best
universe
world
most

```{r}
NextWordPredictor("You're the reason why I smile everyday. Can you follow me please? It would mean the", 3, " ")
```

confirmed answer is world

3.)  Hey sunshine, can you follow me and make me the


happiest
smelliest
bluest
saddest

```{r}
NextWordPredictor("Hey sunshine, can you follow me and make me the", 2, " ")
```

confirmed answer is happiest

4.)  Very early observations on the Bills game: Offense still struggling but the


defense
players
crowd
referees

```{r}
a <- NextWordPredictor("Very early observations on the Bills game: Offense still struggling but the", 2, " ")
a[grepl("crowd", names(a))] # crowd = 27, crowds = 7, crowd's = 2, crowded = 1 
a[grepl("players", names(a))] # players = 18, players = 1 (again??)
a[grepl("defense", names(a))] # defense = 16, defenseman = 1, defense = 1
```

answer is not crowd
answer is not players

5.)  Go on a romantic date at the


beach
grocery
movies
mall

```{r}
NextWordPredictor("Go on a romantic date at the", 2, " ")
```

confirmed answer is beach

6.)  Well I'm pretty sure my granny has some old bagpipes in her garage I'll dust them off and be
on my

phone
way
motorcycle
horse

```{r}
a <- NextWordPredictor("Well I'm pretty sure my granny has some old bagpipes in her garage I'll dust them off and be on my", 2, " ")
a[grepl("phone", names(a))] # 701
a[grepl("way", names(a))] #2136

```

confirmed answer is way

7.) Ohhhhh #PointBreak is on tomorrow. Love that film and haven't seen it in quite some

thing
weeks
years
time

```{r}
NextWordPredictor("Ohhhhh #PointBreak is on tomorrow. Love that film and haven't seen it in quite some", 2, " ")
```

confirmed answer is time

8.)  After the ice bucket challenge Louis will push his long wet hair out of his eyes with his little

toes
eyes
ears
fingers

```{r}
a <- NextWordPredictor("After the ice bucket challenge Louis will push his long wet hair out of his eyes with his little", 2, " ")
a[grepl("fingers", names(a))] #3
a[grepl("ears", names(a))] #1
a[grepl("eyes", names(a))] #1
```

answer is not ears
confirmed answer is fingers

9.)  Be grateful for the good times and keep the faith during the

bad
sad
hard
worse

```{r}
a <- NextWordPredictor("Be grateful for the good times and keep the faith during the", 2, " ")
a[grepl("bad", names(a))] # bad = 4x
a[grepl("hard", names(a))] # hard = 4, hardest = 1, hard = 1 (again??), harder = 1
```

answer is not hard
confirmed answer is bad

10.)  If this isn't the cutest thing you've ever seen, then you must be

insane
asleep
insensitive
callous

```{r}
a <- NextWordPredictor("If this isn't the cutest thing you've ever seen, then you must be", 2, " ")
a[grepl("insane", names(a))] #insane = 4
```

confirmed answer is insane
