---
title: "Qz3"
output: html_document
---

These file paths are for the desktop running Windows 7.


```{r echo=FALSE}
# library(stringi)
# library(tm) 
# library(quanteda)
# library(RWeka)
# library(tm)
# library(tau)
# 
# 
# enBlogs <- stri_read_lines("~/LL/Coursera/Courses/Capstone/Coursera-SwiftKey/final/en_US/en_US.blogs.txt")
# set.seed(100)
# enBlogsSubset <- sample(enBlogs, size=length(enBlogs)*.05, replace=FALSE)
#     
# enTwitter <- readLines("~/LL/Coursera/Courses/Capstone/Coursera-SwiftKey/final/en_US/en_US.twitter.txt")
# set.seed(100)
# enTwitterSubset <- sample(enTwitter, size=length(enTwitter)*.05, replace=FALSE)
#     
# enNews <- stri_read_lines("~/LL/Coursera/Courses/Capstone/Coursera-SwiftKey/final/en_US/en_US.news.txt")
# set.seed(100)
# enNewsSubset <- sample(enNews, size=length(enNews)*.05, replace=FALSE)
#    
# subset <- c(enBlogsSubset, enTwitterSubset, enNewsSubset)
# saveRDS(subset, "~/LL/Coursera/Courses/Capstone/Subsets/subset05.rds")
# input <- strsplit(subset, "[,.:;?!]\\s*")
# corpus <- Corpus(VectorSource(input))
# inputClean <- tm_map(corpus, removeNumbers)
# inputClean <- tm_map(inputClean, removeWords, stopwords("english")) 
# inputClean <- tm_map(inputClean, removePunctuation)
# inputClean <- tm_map(inputClean, content_transformer(tolower))
# inputClean <- tm_map(inputClean, stripWhitespace)
# tdm <- TermDocumentMatrix(inputClean)
# saveRDS(tdm, "~/LL/Coursera/Courses/Capstone/Subsets/tdm05.rds")
```

```{r echo=FALSE}
library(stringi)
library(tm) 
library(quanteda)
library(RWeka)
library(tm)
library(tau)


###########################################################
############## Trying to use Correlation ##################
###########################################################
# tdm <- readRDS("~/LL/Coursera/Courses/Capstone/Subsets/tdm05.rds")
# system.time(live.05 <- findAssocs(tdm, "live and", .05))
# #live.05 <- order(live.01[-live.01$live])
# live.05 <- live.05$live
# grep("sleep", names(live.05)) #no
# grep("die", names(live.05)) #no
# grep("eat", names(live.05))
# grep("give", names(live.05))


###########################################################
############## using keywords plus one approach ###########
###########################################################


NextWord <- function(a = char()){
        subset <- readRDS("~/LL/Coursera/Courses/Capstone/Subsets/subset50.rds")
        options(warn=-1)
        string <- grep(a, subset)
        awords <- strsplit(a, " ")
        
        if(length(string) == 0){ 
                library(tm)
                tdm <- readRDS("~/LL/Coursera/Courses/Capstone/Subsets/tdm05.rds")
                firstTwo <- c(awords[[1]][1], awords[[1]][2])
                firstTwo <- paste(firstTwo, collapse=" ")
                lastTwo <- c(awords[[1]][length(awords[[1]])-1], awords[[1]][length(awords[[1]])])
                lastTwo <- paste(lastTwo, collapse=" ")
                firstTwoCor <- findAssocs(tdm, firstTwo, .01)
                lastTwoCor <- findAssocs(tdm, lastTwo, .01)
                if (length(firstTwoCor)< 2) {stop("shorten the string")} 
                if (length(lastTwoCor) < 2){stop("shorten the string")}
                print(firstTwoCor)
                print(lastTwoCor)}
        
        sentences <- strsplit(subset[string], " ")
        locations <- as.integer()
        words <- as.character()
        for (i in 1:length(sentences)){
                locations <- grep(awords[[1]][1], sentences[[i]]) + length(awords[[1]])
                words[i] <- sentences[[i]][locations]
        }
        final <- sort(table(words), decreasing=TRUE)
        return(final)
        final
}

```



1.) When you breathe, I want to be the air for you. I'll be there for you, I'd live and I'd

sleep
die
eat
give

```{r echo=FALSE}
NextWord("live and")
```

die

2.)  Guy at my table's wife got up to go to the bathroom and I asked about dessert and he started telling me about his

spiritual
horticultural
financial
marital

```{r echo=FALSE}
NextWord("about his")
grep("spiritual", NextWord("about his"))
grep("horticultural", NextWord("about his"))
grep("financial", NextWord("about his"))
grep("marital", NextWord("about his"))
```

marital

3.)  I'd give anything to see arctic monkeys this

weekend
morning
month
decade

```{r echo=FALSE}
NextWord("monkeys this")

```

weekend? pure guess

4.)  Talking to your mom has the same effect as a hug and helps reduce your

sleepiness
happiness
stress
hunger

```{r echo=FALSE}
NextWord("reduce your")
```

stress

5.)  When you were in Holland you were like 1 inch away from me but you hadn't time to take a

minute
walk
picture
look

```{r echo=FALSE}
NextWord("to take a")
```

picture

6.)  I'd just like all of these questions answered, a presentation of evidence, and a jury to settle the

case
matter
account
incident

```{r echo=FALSE}
NextWord("settle the")
```

case is confirmed wrong
matter

7.)  I can't deal with unsymetrical things. I can't even hold an uneven number of bags of groceries in 

each
arm
hand
finger
toe

```{r echo=FALSE}
NextWord("groceries in each")
grep("arm", NextWord("each"))
grep("hand", NextWord("each"))
grep("finger", NextWord("each"))
grep("toe", NextWord("each"))
```

hand

8.)  Every inch of you is perfect from the bottom to the

center
top
middle
side

```{r echo=FALSE}
NextWord("bottom to the")
```

top

9.)  I'm thankful my childhood was filled with imagination and bruises from playing

weekly
outside
daily
inside

```{r echo=FALSE}
NextWord("playing")
```

outside

10.)  I like how the same people are in almost all of Adam Sandler's

novels
movies
pictures
stories

```{r echo=FALSE}
NextWord("Adam Sandler")
```

movie



